Analysis of finite-volume advection schemes on cubed-sphere grids and an accurate \textcolor{red}{scheme} for divergent winds

### 2024-05-21 paper.tex
added abstract

%% Abstract
\begin{abstract}
%% Text of abstract
To be written.
\end{abstract}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{intro}
The Finite Volume Cubed-Sphere Dynamical Core (FV3), developed by the Geophysical Fluid Dynamics Laboratory (GFDL) and the National Oceanic and Atmospheric Administration (NOAA), 
has been embraced as the dynamical core for several atmospheric models (cf. eg. \cite{zhou:2015,lee:2020, bertrand:2020,harris:2020,martin:2022,zhang:2024}).
In 2019, FV3 attained significant recognition when it was adopted as the new dynamical core for the Global Forecast System the U.S. National Weather Service (NWS), replacing the spectral transform GFS.
Additionally, FV3 is used in the Hurricane Analysis and Forecast System (HAFS) from the NWS for tropical cyclone forecasts \cite{dong:2020}.
 % (\url{https://www.noaa.gov/media-release/noaa-upgrades-us-global-weather-forecast-model}, last
%accessed on April 19th, 2024).

>>>>

%% Abstract
\begin{abstract}
%% Text of abstract
The cubed-sphere finite-volume dynamical core (FV3), developed by GFDL-NOAA-USA, serves as the dynamical core for many models worldwide. 
In 2019, it was officially designated as the dynamical core for the new Global Forecast System of the National Weather Service in the USA, replacing the spectral model.
The finite-volume approach employed by FV3 to solve horizontal dynamics involves the application of transport finite-volume fluxes for different variables. 
Hence, the transport scheme plays a key role in the model.
Therefore, this work proposes to revisit the details of the transport scheme of FV3 with the aim of adding enhancements.
We proposed modifications to the FV3 transport scheme, which notably enhanced accuracy, particularly in the presence of divergent winds, as evidenced by numerical experiments. 
In contrast to the FV3 scheme's first-order accuracy in the presence of divergent winds, the proposed scheme achieves second-order accuracy.
For divergence-free winds, both schemes are second-order, with our scheme being slightly more accurate.
Additionally,  the proposed scheme requires only a small additional computational effort and are of simple implementation in the existing codes.
In summary, the proposed scheme offer significant improvements in accuracy, particularly in the presence of divergent winds, which are present in some atmospheric phenomena, while maintaining computational efficiency.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{intro}
The Finite Volume Cubed-Sphere Dynamical Core (FV3), developed by the Geophysical Fluid Dynamics Laboratory (GFDL) and the National Oceanic and Atmospheric Administration (NOAA), 
has been embraced as the dynamical core for several atmospheric models (cf. eg. \cite{zhou:2015,lee:2020, bertrand:2020,harris:2020,martin:2022,zhang:2024}).
In 2019, FV3 attained significant recognition when it was adopted as the new dynamical core for the Global Forecast System the U.S. National Weather Service (NWS), replacing the spectral transform dynamical core.
Additionally, FV3 is used in the Hurricane Analysis and Forecast System (HAFS) from the NWS for tropical cyclone forecasts \cite{dong:2020}.
 % (\url{https://www.noaa.gov/media-release/noaa-upgrades-us-global-weather-forecast-model}, last
%accessed on April 19th, 2024).
